\documentclass[line, margin]{res}
% \usepackage[a4paper, margin=1.5cm, right=4.5cm]{geometry}
\usepackage{hyperref}

\usepackage{enumitem}
\usepackage{color}
\usepackage{url}
\definecolor{darkblue}{rgb}{0,0,0.5}
\hypersetup{
    breaklinks=true,
    pdfauthor={Ng Guoyou},
    pdftitle={Ng Guoyou --- Resume},
    colorlinks=true,
    linktoc=all,
    urlcolor=darkblue,
    linkcolor=darkgray,
    citecolor=black,
    pdfborder={0 0 0}
}

\newcommand{\at}[0]{@}

\begin{document}
\name{\huge{Ng Guoyou}}
\address{
    \href{mailto:ng.guoyou+cv\at gmail.com}{ng.guoyou\at gmail.com}
    \href{https://github.com/gyng}{github.com/gyng}
    % \href{https://www.linkedin.com/in/guoyou}{www.linkedin.com/in/guoyou}
}

\begin{resume}
    % \section{BUZZWORDS}
    %     Work experience with TypeScript, Rust, Python, JavaScript, Node.js, Ruby, HTML, CSS, Docker, React, Redux, Webpack, Photoshop, Illustrator, Agile, user testing

    \section{EXPERIENCE}
        \textbf{BASIS AI (acquired by AICADIUM)} \\
        \textbf{Software Engineer}, Singapore, Jan 2019--Oct 2020, Jun 2021--Present \\
        \textit{TypeScript, Python, Rust, Webpack, React, Redux, Docker, Kubernetes, UX} \\
        Employee \#3. Full stack developer on a \href{https://docs.basis-ai.com/}{machine learning platform} for training and deployment of data science workloads.
        Main contributor to frontend with Webpack, TypeScript, React$+$Redux. Created reusable React component library.
        Built performant client workload monitor in async Rust; includes streaming ZIP and large file uploads.
        Developed backend features in Python such as pagination and RBAC.
        Implemented Docker image caching for fast workloads using \href{https://github.com/GoogleContainerTools/kaniko}{kaniko}.
        Implemented company website \href{https://basis-ai.com/}{basis-ai.com} in Next.js.
        Set up agile environment and processes.
        Conducted basic UX research and user testing.
        Built product PoCs around CV and ML.
    
        \textbf{CREDIT SUISSE} \\
        \textbf{Software Engineer}, Singapore, Nov 2020--Jun 2021 \\
        \textit{TypeScript, React, Redux, MobX, Webpack} \\\
        Maintained and implemented features for internal financial applications and platforms around securities order placement, disclosures, and tracking. Modernised and refactored legacy frontend applications.

        \textbf{GOVTECH (GOVERNMENT TECHNOLOGY AGENCY)} \\
        \textbf{Software Engineer}, Singapore, Jan 2016--Jan 2019
        \\
        \textit{\href{https://foodservices.gobusiness.gov.sg/licences/foodservices}{GoBusiness Licensing guided journey}, government licenses portal} \\
        \textit{2019. TypeScript, React, Redux, Kotlin, Spring Boot} \\
        Part of initial team. Bootstrapped project and implemented features for F\&B licensing.
        
        \textit{\href{https://www.mycareersfuture.sg}{www.mycareersfuture.sg}, job portal} \\
        \textit{2018. Node, TypeScript, JavaScript, React, Redux} \\
        Implemented frontend features for MyCareersFuture. Orchestrated transition to TypeScript across the team. Bootstrapped greenfield employer module with TypeScript.

        \textit{\href{https://opencerts.io/}{opencerts.io}, academic qualification verifier} \\
        \textit{2018. Ethereum, Parity, Solidity, JavaScript, TypeScript, React, Redux} \\
        Created tools to bulk-register academic transcripts on Ethereum and interact with smart contracts in Node, TypeScript and React.

        \textit{Data ingestion validator, API endpoint, and data visualisation application} \\
        \textit{2017. Rust, Python, Flask, JavaScript, React, Redux} \\
        Optimised data ingestion time by 50$\times$ over Python implementation using Rust.
        Developed front-end application for geographic data from scratch with IE11 support.

        \textit{\href{https://www.businessgrants.gov.sg/}{www.businessgrants.gov.sg}, grant application and tracking portal} \\
        \textit{2016. Ruby on Rails, React, Redux} \\
        Implemented features for and fixed bugs on forms with complex validation logic.
        Integrated with SAML.
        Introduced linting for Ruby and JavaScript on large codebase.

        \pagebreak

        \textbf{ROOMORAMA} \\
        \textbf{Intern, Software Engineer}, Singapore, May 2013--Aug 2013 \\
        Built a business intelligence dashboard in Ruby and CoffeeScript. Worked on the main Ruby On Rails application implementing features and bug fixes.

        % \textit{Freelance} \\
        % \textit{Web Designer}, 2012--2014 \\
        % Worked with several clients on short-term jobs to design and implement web designs as a freelance contractor. Used HTML, CSS and JavaScript for frontend projects. Interacted with clients to fulfill their business requirements. Amount of design ranged from created-from-scratch to adaptations of existing designs for the web.

        % \textbf{SINGAPORE ARMED FORCES} \\
        % \textbf{Armourer}, Singapore, Dec 2008--Dec 2010 \\
        % Served National Service as an armourer. Was responsible for managing the logistics and maintenance for an armoury. Partially automated daily report generation in Excel.

    \section{EDUCATION}
        Bachelor of Computing (Communications \& Media) Hons. \\
        National University of Singapore, 2011--2015 \\
        UX, HCI, and computer graphics focus

    \section{PERSONAL}
        Singapore citizen. Native English and Mandarin Chinese speaker.
        \\
        \begin{itemize}[leftmargin=*]
        \itemsep0em 
        \item \href{https://github.com/gyng/synthrs}{Toy audio synthesizer library in Rust with MIDI support and WebAssembly interface}
        \item \href{https://github.com/gyng/ditherer}{Retro image filtering application in React and Redux}
        \item \href{https://github.com/gyng/rust-raytracer}{Parallel raytracer with basic animations in Rust}
        \item \href{https://github.com/gyng/save-in}{Browser extension for organising downloads with $>$3000 users}
        \item \href{https://github.com/gyng/betabot}{Chatbot for IRC, Slack, Discord in Ruby with a plugin system}
        \item \href{https://github.com/gyng/book}{Sharing sessions and presentations}
        \end{itemize}
        More projects on \href{https://github.com/gyng}{GitHub}.

        % Source code and demos available on \href{https://github.com/gyng}{GitHub}.

\end{resume}
\end{document}
